### 2016-06-25 store-consistency.tex

\subsection{Store Consistency}
\label{sec:store-consistency}

@@

>>>>

\section{Store Consistency}
\label{sec:store-consistency}

@@

\subsection{Eventually Consistent Replication}

\begin{figure}
\centering
\subcaptionbox {
  Replica model
  \label{fig:ec-theirs}
} [
  0.4\columnwidth
] {
  \includegraphics[scale=0.7]{Figures/ec-theirs}

}
\hspace*{0.1in}
\subcaptionbox {
  Subset model
  \label{fig:ec-ours}
}{
  \includegraphics[scale=0.45]{Figures/ec-ours}
} \caption{In the replica model, operation $\op$ generates effect
$\eta$ at replica $R_1$, which is then merged to $R_2$. If the
\emph{store is {\sc cc}}, then $R_2$'s state at merge event is same or
larger than $R_1$'s state at generation event (the difference is
highlighted). In our subset model, $\op$ witnesses $S_1 \subseteq
\E.\A$ and generates $\eta$, which is immediately added to $\E.\A$. A
later operation may witness $S_2 \subseteq \E.\A$, and if the
\emph{operation is} {\sc cc} and $\eta \in S_2$, then it also
witnesses $S_1$ (i.e., $S_1 \subseteq S_2$). } 
% Moreover, Like $R_2 - R_1$, if all effects in $S_2 - S_1$ are
% concurrent with $\eta$, i.e., $\not\exists\eta'.~\eta' \in S_2 - S_1
% \conj % visZ(\eta,\eta')$, then any precondition $P$ that is valid
% when $\op$ executed is also valid when $\eta$ is witnessed because
% of the stability condition.
\label{fig:ec-theirs-vs-ours}
\end{figure}

In this section, we present an intuitive explanation of the soundness
result in context of eventually consistent replication. 
% In other words, we explain why our approach is a sound way of
% reasoning about transactions under eventually consistent replication
% despite our system model not including the standard artifacts
% associated with a replicated store.

Existing approaches to reason about eventually consistent replication
necessarily involve reasoning in terms of \emph{replicas} of data. The
primary challenge in this setting is to ensure that the assumptions
made and guarantees enforced by an operation at one replica carry over
to other replicas that merge its effects, thus preserving the overall
integrity of the system. Reasoning frameworks, such
as~\cite{gotsmanpopl16}, address this challenge by imposing
restrictions on how various replica states differ, i.e., by
strengthening the consistency of the store. Our view of eventually
consistent replication however does not explicitly involve replicas.
Fig.~\ref{fig:ec-theirs-vs-ours} contrasts our model of EC replication
with the conventional replica-based model.  Under our model, the
notion of a replica is subsumed by the concept of visibility; a
replica is defined by the subset ($S$) of global state ($\E.\A$) that
an operation witnesses.  Constraints over replica states therefore
manifest as constraints over the visibility relation. For example,
instead of requiring the store to be causally consistent, an operation
can request to witness a causally consistent subset of the state; such
demands can be made via the trace invariant $\I$. For a precondition
($P$) of the operation to be useful, it has to be an assertion over
every causally consistent subset of the global state. Since any
replica that eventually executes the operation has to expose one such
subset ($S$), the precondition is guaranteed to hold regardless of the
replica. There is however one problem with this explanation; by
considering subsets of just one global state, it ignores the fact that
the global state (hence, the replica states) change during the
execution of the operation. Existing approaches account for this
change by distinguishing between \emph{effect generation} event at one
replica and \emph{effect merge} event at another replica, and
requiring that certain invariants be preserved between these two
events at different replicas. Our framework folds all of this into a
stability condition (\S\ref{sec:rely-guarantee}). Since any change to
the global state during the execution of the operation is an
interference, and $P$ is required to be stable with respect to any
such interference, it follows that $P$ is valid on every replica, thus
ensuring that assumptions made at the generation event are also valid
at the merge event.

\subsection{Example}

\GK{Here, I plan to include the full example that we dropped from
\S\ref{sec:motivation}.}
